---
title: "Memory's reflection of learned information value increases across development: Experiment 2 analyses"
author: "Kate Nussenbaum (katenuss@nyu.edu)"
date: "7/18/19"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

<style type="text/css">

h1.title {
  font-size: 38px;
}
h1 { /* Header 1 */
  font-size: 28px;
}
h2 { /* Header 2 */
    font-size: 22px;
}
h3 { /* Header 3 */
  font-size: 18px;
}

</style>



```{r setup, include = F}
knitr:: opts_chunk$set(cache = TRUE, echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width='600px', out.height = '300px', dpi=600, fig.align='center')
```

```{r libraries and paths}
## SECTION 0: Set everything up

# Load needed libraries
library(tidyverse)
library(magrittr)
library(afex)
library(glue)
library(readxl)
library(lmSupport)
library(pander)
library(sjPlot)
library(optimx)
library(kableExtra)
library(jtools)
library(brms)

#label data folders
dataFolder <- "recoded_data/" #Experiment 2 data
exp1DataFolder = "../../githubProject/E1_anonymized_data/" #Experiment 1 data

```

```{r create ggplot theme}
#create standard theme to use for ggplot
kate.theme <- theme(panel.background = element_rect(fill='transparent'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=16, vjust=-.25),
                        axis.title.y = element_text(size=16, vjust=1, margin = margin(r = 10)),
                        axis.text.x = element_text(size=12, colour="black"),
                        axis.text.y = element_text(size=12, colour="black"),
                        panel.spacing.x = unit(1, "lines"),
                        panel.border = element_rect(colour = "black", fill=NA, size=1),
                        legend.key=element_blank(),
                        legend.text=element_text(size=12),
                        legend.title = element_text(size = 14),
                        plot.title = element_text(size=16, face = "bold", hjust = .5), 
                        strip.text.x = element_text(size=12), 
                        strip.text.y = element_text(size=12, face="bold"), 
                        strip.background = element_rect(colour= "black", fill = "transparent"))


#Define 3 theme colors to use
color1 = "#78C2C3"
color2 = "#3F6699"
color3 = "#0D1B4C"
```

```{r scale function}
#define new function so that scale returns a vector, not a matrix
scale_this <- function(x) as.vector(scale(x))
```

```{r import task data}
# READ IN TASK DATA #

#identify relevant data files
freqfiles = list.files(dataFolder, pattern = "freqTask")
PAfiles = list.files(dataFolder, pattern = "PA")
memTestFiles = list.files(dataFolder, pattern = "mem..txt")
memTestGridFiles = list.files(dataFolder, pattern = "Grid")
freqReports= list.files(dataFolder, pattern = "freqReports")

#frequency data
freqData <- tibble(filename = freqfiles) %>%
  mutate(file_contents = map(filename, ~ read_tsv(file.path(dataFolder, .), col_names = c("item", "freqCond", "freqResp", "freqRT", "X5", "X6", "freqTrial")))) %>%
  separate(filename, into = c("filename", "block"), sep = "k") %>%
  separate(block, into = c("block", "junk"), sep = ".txt") %>%
  separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
  unnest() %>%
  select(-matches("X")) %>%
  group_by(sub, item, block) %>% 
  mutate(stimNum = 1, freqAppearanceCount = cumsum(stimNum))  #add appearance count

#paired associates data
paData <- tibble(filename = PAfiles) %>%
  mutate(file_contents = map(filename, ~ read_tsv(file.path(dataFolder, .), col_names = c("paAssociate", "item", "associateSide", "paResp", "paRT", "X6", "X7", "paTrial" )))) %>%
  separate(filename, into = c("filename", "block"), sep = "PA") %>%
  separate(block, into = c("block", "junk"), sep = ".txt") %>%
  separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
  unnest() %>%
  select(-matches("X"))

#memory test data
memData <- tibble(filename = memTestFiles) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(dataFolder, .), col_names = c("item", "X2", "X3", "memRT", "memResp", "X6", "X7")))) %>%
    separate(filename, into = c("filename", "block"), sep = "mem") %>%
    separate(block, into = c("block", "junk"), sep = ".txt") %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
    unnest() %>%
  select(-matches("X"))

#memory test grids
memGrids <- tibble(filename = memTestGridFiles) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(dataFolder, .), col_names = c("paAssociate", "gridLocation")))) %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename")) %>%
    unnest()

#frequency reports data
freqReportsData <- tibble(filename = freqReports) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(dataFolder, .), col_names = c("item", "X2", "X3", "freqReportRT", "memFreqResp", "X6", "X7")))) %>%
    separate(filename, into = c("filename", "block"), sep = "mem") %>%
    separate(block, into = c("block", "junk"), sep = "_freqReports.txt") %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
    unnest() %>%
  select(-matches("X"))
       
#get mean and sd of frequency reports for each subject for each block
freqRespSubMeans <- freqReportsData %>%
  group_by(sub, block) %>%
  summarize(meanFreqResp = mean(memFreqResp), sdFreqResp = sd(memFreqResp))

#join with freqReports data and compute z score
freqReportsData <- full_join(freqReportsData, freqRespSubMeans, by = c("sub", "block")) %>%
  mutate(freqRespZ = (memFreqResp - meanFreqResp)/sdFreqResp)

#join memory data and pa data
memData <- full_join(memData, paData, by = c("sub", "item", "block"))

#join memory data and memory grid data
memData <- full_join(memData, memGrids, by = c("sub", "paAssociate"))

#join memory data and frequency reports
memData <- full_join(memData, freqReportsData, by = c("sub", "block", "item"))

#compute frequencies for each item for each subject
frequencies <-freqData %>% 
  group_by(sub, block, item) %>% 
  summarise(freqCond = mean(freqCond))
  
#join frequency condition with memory data
memData <- full_join(memData, frequencies, by = c("sub", "block", "item"))

#remove rows from memDat which just have memory test lures
memData %<>%
  filter(!is.na(item))

#Now we have two dataframes with all of our task data: memData and freqData
```

```{r import subject information}
#read in excel sheet with subject information
subInfo <- read_excel(glue("{dataFolder}/E2subInfo.xlsx"))  %>%
  mutate_at(.vars = vars(sub), .fun = as.character)

#Join subject info into mem data frame and freq data frame
memData <- full_join(memData, subInfo, by = "sub")
freqData <- full_join(freqData, subInfo, by = "sub") 
```


```{r paired associates exclusion}
## Identify and exclude subjects who performed below chance (50%) on paired associates task ##

#Compute PA accuracy for each trial for each subject
paData %<>% 
  mutate(acc = case_when(paResp - associateSide == 0 ~ 1, paResp - associateSide != 0 ~ 0))

#Compute PA accuracy for each subject for each block - have to respond correctly 75% of the time or more to be statistically above chance
paAccData.subBlocks <- paData %>% 
  group_by(sub, block) %>% 
  summarize(meanPaAcc = mean(acc)) %>% 
  mutate(include = case_when(meanPaAcc > .74 ~ 1, meanPaAcc <.75 ~ 0))

#Spread include so that there is an include1 and include2 columns and identify subjects who should be excluded from either block
paAccData.sub <- paAccData.subBlocks %>% 
  select(-meanPaAcc) %>% 
  spread(block, include) %>% 
  rename(include1 = `1`, include2 = `2`) %>% 
  mutate(include = case_when(include1 + include2 == 2 ~ 1, include1 + include2 < 2 ~0)) %>% select(-c(include1, include2))

#identify the sub ID of the excluded subs
excludedSubs <- paAccData.sub %>%
  filter(include == 0)
excludedSubIDs = excludedSubs$sub

#Remove excluded subs from paData, subInfo, memData, freqData
subInfo %<>% filter(sub != excludedSubIDs)
memData %<>% filter(sub != excludedSubIDs)
freqData %<>% filter(sub != excludedSubIDs)

#compute mean and sd of included subs
paStats <- paAccData.subBlocks %>% 
  group_by(include) %>%
  summarize(grandMeanPaAcc = mean(meanPaAcc), sdPaAcc = sd(meanPaAcc), minPaAcc = min(meanPaAcc))

```

# Subject statistics
```{r sub stats}
# get mean and sd age
subStats <- subInfo %>% 
  summarise(meanAge = mean(age), sdAge = sd(age), minAge = min(age), maxAge = max(age), n = n(), numFemales = sum(gender))

pander(subStats)
```

# Confirmatory analyses: Experiment 2
## Frequency-learning task 
### Frequency task accuracy
```{r compute frequency task accuracy}
#compute accuracy for each trial
freqData %<>% 
  mutate(freqAcc = case_when(freqResp == 0 & freqAppearanceCount == 1 ~ 1, freqResp == 0 & freqAppearanceCount > 1 ~ 0, freqResp == 1 & freqAppearanceCount > 1 ~ 1, freqResp == 1 & freqAppearanceCount == 1 ~ 0))

#split data based on whether it was the first presentation or repeated presentation
freqDataFirst <- freqData %>%
  filter(freqAppearanceCount == 1)

freqDataRepeated <- freqData %>%
  filter(freqAppearanceCount >1)

#for repeated presentation, compute mean accuracy in frequency task for each subject
freqDataSubBlockMeans <- freqDataRepeated %>% 
  group_by(sub, block, age) %>% 
  summarise(N = n(), meanSubAcc = mean(freqAcc, na.rm = TRUE)) %>% 
  arrange(meanSubAcc) %>%
  mutate(badFreqSub = case_when(meanSubAcc < .10 ~ 1, meanSubAcc > .10 ~ 0))

#display table of means
freqDataSubBlockMeans %>% arrange(meanSubAcc)

#merge data frames
freqAccData <- merge(freqData, freqDataSubBlockMeans, by = c("sub", "block", "age"), all = TRUE)

#remove subjects who performed poorly in the frequency task
freqAccDataFiltered <- freqAccData %>%
  filter(meanSubAcc > .10) %>%
  droplevels()
```


```{r first appearance count freq acc display means and process data}
#set block, subject, item as factors
freqAccDataFiltered$sub <- as.factor(freqAccDataFiltered$sub)
freqAccDataFiltered$item <- as.factor(freqAccDataFiltered$item)
freqAccDataFiltered$block <- as.factor(freqAccDataFiltered$block)

#re-split based on first vs. repeated appearance
freqDataFirst <- freqAccDataFiltered %>%
  filter(freqAppearanceCount == 1)
  
freqDataRepeated <- freqAccDataFiltered %>%
  filter(freqAppearanceCount > 1)

#compute mean and sd
freqAccFirstStats <- freqDataFirst %>%
  summarize(meanAcc = mean(freqAcc), sdAcc = sd(freqAcc))
pander(freqAccFirstStats)

#compute mean and sd
freqAccRepeatedStats <- freqDataRepeated %>%
  summarize(meanAcc = mean(freqAcc), sdAcc = sd(freqAcc))
pander(freqAccRepeatedStats)
```


#### Frequency accuracy mixed-effects model: New items
```{r first appearance count freq acc maximal model, eval = F}
freqFirstAppearanceAcc.maximal <- mixed(freqAcc ~ block + (block|sub) + (block|item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r first appearance count freq acc model 2}
#remove correlations and try again
freqFirstAppearanceAcc.2 <- mixed(freqAcc ~ block + (block||sub) + (block||item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re =T)

#display mixed output
nice(freqFirstAppearanceAcc.2)

#return glmer output
freqFirstAppearanceAcc.2.glmer <- mixed(freqAcc ~ block + (block||sub) + (block||item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re =T, return = "merMod")

#display glmer output
summ(freqFirstAppearanceAcc.2.glmer)
```


#### Frequency accuracy mixed-effects model: Repeated items
```{r first appearance count freq acc scale variables}
freqDataRepeated$appearanceCountScaled <- scale_this(freqDataRepeated$freqAppearanceCount)
```

```{r freq acc maximal model}
freqAcc.maximal <- mixed(freqAcc ~  block * appearanceCountScaled + (block* appearanceCountScaled|sub) + (block * appearanceCountScaled|item), data = freqDataRepeated, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

nice(freqAcc.maximal) 

#return glmer output
freqAcc.maximal.glmer <- mixed(freqAcc ~  block * appearanceCountScaled + (block* appearanceCountScaled|sub) + (block * appearanceCountScaled|item), data = freqDataRepeated, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod")

summ(freqAcc.maximal.glmer)
```


### Frequency task reaction times:
#### Frequency reaction times mixed-effects model: Repeated items
```{r frequency task RT data processing}
#Filter out inaccurate trials
freqRTdata <-freqDataRepeated %>%
  filter(freqAcc == 1)

#Scale appearance count
freqRTdata$appearanceCountScaled <- scale_this(freqRTdata$freqAppearanceCount)
```

```{r frequency task RT maximal model}
freqRT.maximal <- mixed(freqRT ~  appearanceCountScaled * block + (appearanceCountScaled * block|sub) + (appearanceCountScaled * block|item), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

nice(freqRT.maximal)

#return lmer results
freqRT.maximal.lmer <- mixed(freqRT ~  appearanceCountScaled * block + (appearanceCountScaled * block|sub) + (appearanceCountScaled * block|item), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod")

summ(freqRT.maximal.lmer)
```

#### Plot: Frequency task reaction times
```{r freqRT interaction plot}
freqRTPlotData <- freqRTdata %>% 
  group_by(freqAppearanceCount, block) %>% 
  summarise(meanFreqRT = mean(freqRT, na.rm = T), sdFreqRT = sd(freqRT, na.rm = T), N = n(), seRT = sdFreqRT/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanFreqRT + seRT, ymin = meanFreqRT - seRT)

#make plot
freqRTPlot <- ggplot(freqRTPlotData, aes(x = freqAppearanceCount, y = meanFreqRT, fill = block)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c(color1, color3)) +
  geom_errorbar(errorBars, position = position_dodge(width = .9), width = .1) +
  xlab("Appearance Count") +
  ylab("Frequency Task Reaction Times (s)") +
  ggtitle("Frequency Task Reaction Times") + 
  kate.theme
freqRTPlot
```


## Explicit frequency reports
```{r compute freq response error}
#compute response error and response error magnitude
memData %<>% 
  mutate(memFreqRespError = memFreqResp - as.numeric(as.character(freqCond)), memFreqRespErrorMagnitude = abs(memFreqRespError))

#code frequency condition as a factor
memData$freqCondFactor <- as.factor(memData$freqCond)
```

### Explicit frequency reports mixed-effects model
```{r explicit freq error maximal model}
freqError.maximal <- mixed(memFreqRespErrorMagnitude ~ freqCondFactor *block + (freqCondFactor*block|sub) + (freqCondFactor|item), data = memData, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

nice(freqError.maximal)

#return lmer results
freqError.maximal.lmer <- mixed(memFreqRespErrorMagnitude ~ freqCondFactor *block + (freqCondFactor*block|sub) + (freqCondFactor|item), data = memData, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod")

summ(freqError.maximal.lmer)
```

```{r explicit freq error stats}
#examine means to underestand interaction
freqErrorMeans <- memData %>%
  group_by(block, freqCondFactor) %>%
  summarize(meanError = mean(memFreqRespErrorMagnitude))
pander(freqErrorMeans)
```


### Plot: Frequency report distributions
```{r frequency histograms}
#plot histogram of frequency responses as a function of frequency
meanFreqResp <- memData %>% 
  group_by(freqCond) %>% 
  summarise(meanFreqResp = mean(memFreqResp, na.rm = TRUE))

#make plot
freqRespHist <- ggplot(memData, aes(x = (memFreqResp), color = freqCondFactor, fill = freqCondFactor)) +
  stat_count(position = "identity", alpha = .5) +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_color_manual(values = c(color1, color3), name = "Frequency Condition") + 
  xlab("Reported Frequency") +
  ylab("Number of Responses") +
   scale_x_discrete(limits = c(1:10)) +
  ggtitle("Adults") +
  geom_vline(xintercept = meanFreqResp$meanFreqResp, color = c(color1, color3), size = 1, linetype = "dashed") + 
  kate.theme 
freqRespHist
```


## Memory accuracy
```{r compute memory accuracy}
#compute memory accuracy for each trial
memData %<>%
  mutate(memAcc = case_when(as.character(memResp) == as.character(gridLocation) ~ 1, as.character(memResp) != as.character(gridLocation) ~ 0))
      
#make block a factor
memData$block <- as.factor(memData$block)
```

### Memory accuracy mixed-effects model
```{r memory accuracy maximal model, eval = F}
memAcc.maximal <- mixed(memAcc ~  freqCondFactor * block + (freqCondFactor*block|sub) + (freqCondFactor*block|item), data = memData, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r memory accuracy model 2}
#remove correlations
memAcc.2 <- mixed(memAcc ~  freqCondFactor * block + (freqCondFactor*block||sub) + (freqCondFactor*block||item), data = memData, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(memAcc.2)

#return glmer results
memAcc.2.glmer <- mixed(memAcc ~  freqCondFactor * block + (freqCondFactor*block||sub) + (freqCondFactor*block||item), data = memData, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(memAcc.2.glmer)
```

### Bayesian analysis of memory
```{r memory accuracy BIC Bayes Factor, include = F}
#Use BIC based Bayes Factors
memAcc.full <- mixed(memAcc ~  freqCondFactor + block + (block||sub) + (block||item), data = memData, family = "binomial", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod", expand_re = T)

memAcc.reduced <- mixed(memAcc ~  block + (block||sub) + (block||item), data = memData, family = "binomial", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod", expand_re = T)


BF_BIC = exp((BIC(memAcc.full) - BIC(memAcc.reduced))/2)
```

#### Model comparison without frequency condition interaction
```{r display memory accuracy BIC Bayes Factor}
BF_BIC 
```


#### Model comparison with full model
```{r memory accuracy BIC Bayes Factor full model, include = F}
#Use BIC based Bayes Factors
memAcc.full <- mixed(memAcc ~  freqCondFactor * block + (block*freqCondFactor||sub) + (block*freqCondFactor||item), data = memData, family = "binomial", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod", expand_re = T)

BF_BIC = exp((BIC(memAcc.full) - BIC(memAcc.reduced))/2)
```

```{r display memory accuracy BIC Bayes Factor 2}
BF_BIC 
```

#### Full brms accuracy model
```{r memory accuracy brms model}
#BRMS model
full_brms <- brm(memAcc ~  freqCondFactor * block + (freqCondFactor*block|sub) + (freqCondFactor*block|item), data = memData,  family = "bernoulli", iter = 1e5,  save_all_pars = T)

summary(full_brms)
```

### Plot: Effects of frequency condition and block on memory
```{r memory accuracy plot, fig.width = 10, fig.height = 6}
memPlotData <- memData %>% 
  group_by(freqCondFactor, block) %>% 
  summarise(meanAcc = mean(memAcc, na.rm = T), sdAcc = sd(memAcc, na.rm = T), N = n(), seAcc = sdAcc/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

memAccPlot <- ggplot(memPlotData, aes(x = block, fill = freqCondFactor, y = meanAcc)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(errorBars, position = position_dodge(width = .9), width = .1) +
  #facet_wrap(~ageGroup) +
  coord_cartesian(ylim = c(0, .75)) +
  xlab("Experiment Block") +
  ylab("Memory Accuracy") +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  ggtitle("Memory Accuracy") + 
  kate.theme
memAccPlot
```

### Plot: Effects of frequency condition on memory (individual subjects)
```{r memory accuracy plot 2, fig.width = 10, fig.height = 6}
memPlotData <- memData %>% 
  group_by(sub, freqCondFactor) %>% 
  summarise(meanAcc = mean(memAcc, na.rm = T), sdAcc = sd(memAcc, na.rm = T), N = n(), seAcc = sdAcc/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

memAccPlotSub <- ggplot(memPlotData, aes(x = freqCondFactor, y = meanAcc)) +
  geom_boxplot() +
  geom_point(aes(group = sub), alpha = .1) +
  coord_cartesian(ylim = c(0, 1)) +
  xlab("Frequency Condition") +
  ylab("Memory Accuracy") +
  ggtitle("Memory Accuracy") + 
  kate.theme
memAccPlotSub
```


## Relation between learning environmental statistics and memory encoding
```{r memory and frequency indices}
#create memory benefit index as specified in the pre-registration

  #first compute each subject's average memory performance in the 1 and 5 condition
temp <- memData %>% 
  group_by(sub, freqCond, block, age, IQ) %>% 
  summarise(meanMem = mean(memAcc, na.rm = TRUE))
  
#make frequency condition a column in the table and then compute difference
temp <- spread(temp, freqCond, meanMem) %>%
  mutate(memDiff = `5` - `1`)

#compute overall memory accuracy
temp2 <- memData %>% 
  group_by(sub, block, age) %>% 
  summarise(overallMeanMem = mean(memAcc, na.rm = TRUE))

#merge data frames and compute memBenefitIndex
memBenefit <- full_join(temp, temp2, by = c("sub", "block", "age")) %>% 
  mutate(memBenefitIndex = memDiff / overallMeanMem) %>% 
  select(-c(`5`, `1`, memDiff, overallMeanMem))

#create frequency distance index  as specified in the pre-registration

  #compute mean z score per frequency condition
meanZs <- memData %>% 
  group_by(sub, block, freqCond, age, IQ) %>% 
  summarise(meanFreqRespZ = mean(freqRespZ, na.rm = TRUE))
  
#spread data
freqDist <- spread(meanZs, freqCond, meanFreqRespZ) %>% 
  mutate(freqDist = `5` - `1`) %>% 
  select(-c(`5`, `1`))

#combine with mem benefit index
subIndices <- full_join(memBenefit, freqDist, by = c("sub", "block", "age", "IQ"))

#remove rows where memBenfit is NaN
subIndices %<>%
  filter(!is.na(memBenefitIndex))

#scale frequency distance
subIndices$freqDistScaled <- scale_this(subIndices$freqDist)

```

### Memory benefit mixed effects model
```{r memory benefit by frequency index model}
memBenefit.model <- mixed(memBenefitIndex ~ freqDistScaled *block  + (1|sub), data = subIndices, method = "KR", control = lmerControl(optCtrl=list(maxfun=1e6)))

nice(memBenefit.model)

#return lmer results
memBenefit.model.lmer <- mixed(memBenefitIndex ~ freqDistScaled *block  + (1|sub), data = subIndices, method = "KR", control = lmerControl(optCtrl=list(maxfun=1e6)), return = "merMod")

summ(memBenefit.model.lmer)
```


### Plot: Relation between frequency distance and memory benefit
```{r frequency distance memory benefit plot}
freqDistMemBenefitPlot <- ggplot(subIndices, aes(x = freqDist, y = memBenefitIndex), color = color3, fill = color3) +
  geom_point(color = color3) +
  geom_smooth(method = "lm", color = color3, fill = color3) +
  #facet_wrap(~IQGroup) +
  xlab("Frequency Distance") +
  ylab("Memory Benefit Index") +
  kate.theme
freqDistMemBenefitPlot
```

### Item-level relation between frequency reports and memory mixed-effects model
```{r item-level freq reports and memory data processing}
#scale frequency reports
memData$memFreqRespScaled <- scale_this(memData$memFreqResp)
```

```{r mem freq relation model}
memFreqRelation.maximal <- mixed(memAcc ~ memFreqRespScaled * block + (memFreqRespScaled * block|sub) + (memFreqRespScaled * block| item), data = memData, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

nice(memFreqRelation.maximal)

#return glmer object
memFreqRelation.maximal.glmer <- mixed(memAcc ~ memFreqRespScaled * block + (memFreqRespScaled * block|sub) + (memFreqRespScaled * block| item), data = memData, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), return = "merMod")

summ(memFreqRelation.maximal.glmer)
```


### Plot: Effects of frequency report on memory accuracy
```{r plot memory by explicit frequency (1), fig.align = "center", fig.width = 7, fig.height = 4}
#plot memory by explicit frequency
memByExplicitFreq1 <- memData %>%
  filter(memFreqResp > 0 & freqCond == 1) %>%
  group_by(memFreqResp, freqCond) %>% 
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N))) 

memByExplicitFreq5 <- memData %>%
  filter(memFreqResp > 0 & freqCond == 5) %>%
  group_by(memFreqResp, freqCond) %>% 
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N))) 

accLimits <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color1
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot1 <- ggplot(memByExplicitFreq1, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color1) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color1) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color1) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  ggtitle("1-Frequency Condition") +
  NULL
explicitFreqMemPlot1
```

```{r plot memory by explicit frequency (5), fig.align = "center", fig.width = 7, fig.height = 4, include = TRUE}
#Repeat for 5 frequency condition

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color3
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot5 <- ggplot(memByExplicitFreq5, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color3) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color3) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color3) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  ggtitle("5-Frequency Condition") +
  NULL
explicitFreqMemPlot5

```

```{r plot memory by explicit frequency, fig.align = "center", fig.width = 7, fig.height = 4}
#Both frequency conditions together
memByExplicitFreqCombined <- memData %>%
  filter(memFreqResp > 0) %>%
  group_by(memFreqResp) %>%
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N))) 

accLimits <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color2
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot <- ggplot(memByExplicitFreqCombined, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color2) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color2) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color2) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  ggtitle("Both Frequency Conditions") +
  NULL
explicitFreqMemPlot
```


# Exploratory analyses: Comparison of E1 and E2
```{r label data with experiment}
memData$exp <- 2
freqData$exp <- 2

#store in new DFs
memData_exp2 <- memData
freqData_exp2 <- freqData
```

```{r import experiment 1 data}
#identify relevant data files
freqfiles = list.files(exp1DataFolder, pattern = "freqTask")
PAfiles = list.files(exp1DataFolder, pattern = "PA")
memTestFiles = list.files(exp1DataFolder, pattern = "mem..txt")
memTestGridFiles = list.files(exp1DataFolder, pattern = "Grid")
freqReports= list.files(exp1DataFolder, pattern = "freqReports")

#frequency data
freqData <- tibble(filename = freqfiles) %>%
  mutate(file_contents = map(filename, ~ read_tsv(file.path(exp1DataFolder, .), col_names = c("item", "freqCond", "freqResp", "freqRT", "X5", "X6", "freqTrial")))) %>%
  separate(filename, into = c("filename", "block"), sep = "k") %>%
  separate(block, into = c("block", "junk"), sep = ".txt") %>%
  separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
  unnest() %>%
  select(-matches("X")) %>%
  group_by(sub, item, block) %>% 
  mutate(stimNum = 1, freqAppearanceCount = cumsum(stimNum))  #add appearance count

#paired associates data
paData <- tibble(filename = PAfiles) %>%
  mutate(file_contents = map(filename, ~ read_tsv(file.path(exp1DataFolder, .), col_names = c("paAssociate", "item", "associateSide", "paResp", "paRT", "X6", "X7", "paTrial" )))) %>%
  separate(filename, into = c("filename", "block"), sep = "PA") %>%
  separate(block, into = c("block", "junk"), sep = ".txt") %>%
  separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
  unnest() %>%
  select(-matches("X")) 

#memory test data
memData <- tibble(filename = memTestFiles) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(exp1DataFolder, .), col_names = c("item", "X2", "X3", "memRT", "memResp", "X6", "X7")))) %>%
    separate(filename, into = c("filename", "block"), sep = "mem") %>%
    separate(block, into = c("block", "junk"), sep = ".txt") %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
    unnest() %>%
  select(-matches("X")) %>%
  group_by(sub, item, block) %>% 
  mutate(stimNum = 1, memAppearanceCount = cumsum(stimNum)) %>%  #add appearance count
  filter(memAppearanceCount == 1) #remove later appearances
  
#memory test grids
memGrids <- tibble(filename = memTestGridFiles) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(exp1DataFolder, .), col_names = c("paAssociate", "gridLocation")))) %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename")) %>%
    unnest()

#frequency reports data
freqReportsData <- tibble(filename = freqReports) %>%
    mutate(file_contents = map(filename, ~ read_tsv(file.path(exp1DataFolder, .), col_names = c("item", "X2", "X3", "freqReportRT", "memFreqRespUnfiltered", "X6", "X7")))) %>%
    separate(filename, into = c("filename", "block"), sep = "mem") %>%
    separate(block, into = c("block", "junk"), sep = "_freqReports.txt") %>%
    separate(filename, into = c("sub", "filename"), sep = "_") %>%
  select(-c("filename", "junk")) %>%
    unnest() %>%
  select(-matches("X")) %>% 
  mutate(memFreqResp = case_when(memFreqRespUnfiltered < 1 ~ NaN, memFreqRespUnfiltered > 0 ~ memFreqRespUnfiltered)) %>% #replace weird frequency reports 
  select(-memFreqRespUnfiltered)
       
#get mean and sd of frequency reports for each subject for each block
freqRespSubMeans <- freqReportsData %>%
  group_by(sub, block) %>%
  summarize(meanFreqResp = mean(memFreqResp, na.rm = T), sdFreqResp = sd(memFreqResp, na.rm = T))

#join with freqReports data and compute z score
freqReportsData <- full_join(freqReportsData, freqRespSubMeans, by = c("sub", "block")) %>%
  mutate(freqRespZ = (memFreqResp - meanFreqResp)/sdFreqResp)

#join memory data and pa data
memData <- full_join(memData, paData, by = c("sub", "item", "block"))

#join memory data and memory grid data
memData <- full_join(memData, memGrids, by = c("sub", "paAssociate"))

#join memory data and frequency reports
memData <- full_join(memData, freqReportsData, by = c("sub", "block", "item"))

#compute frequencies for each item for each subject
frequencies <-freqData %>% 
  group_by(sub, block, item) %>% 
  summarise(freqCond = mean(freqCond))
  
#join frequency condition with memory data
memData <- full_join(memData, frequencies, by = c("sub", "block", "item"))

#remove rows from memDat which just have memory test lures
memData %<>%
  filter(!is.na(item))

#add experiment
memData$exp <- 1
freqData$exp <- 1

#Now we have two dataframes with all of our task data: memData and freqData

```

```{r import experiment 1 subject information}
#read in excel sheet with subject information
subInfo <- read_excel(glue("{exp1DataFolder}/subInfo.xlsx"))  %>%
  mutate_at(.vars = vars(sub), .fun = as.character)

#Join subject info into mem data frame and freq data frame
memData <- full_join(memData, subInfo, by = "sub")
freqData <- full_join(freqData, subInfo, by = "sub") 
paData <- full_join(paData, subInfo, by = "sub")

#filter out participants below age 18
memData %<>%
  filter(age > 18.0)

freqData %<>%
  filter(age > 18.0)

paData %<>%
  filter(age > 18.0)
```


```{r paired associates exclusion exp1}
## Identify and exclude subjects who performed below chance (50%) on paired associates task ##

#Compute PA accuracy for each trial for each subject
paData %<>% 
  mutate(acc = case_when(paResp - associateSide == 0 ~ 1, paResp - associateSide != 0 ~ 0))

#Compute PA accuracy for each subject for each block - have to respond correctly 75% of the time or more to be statistically above chance
paAccData.subBlocks <- paData %>% 
  group_by(sub, block) %>% 
  summarize(meanPaAcc = mean(acc)) %>% 
  mutate(include = case_when(meanPaAcc > .74 ~ 1, meanPaAcc <.75 ~ 0))

#Spread include so that there is an include1 and include2 columns and identify subjects who should be excluded from either block
paAccData.sub <- paAccData.subBlocks %>% 
  select(-meanPaAcc) %>% 
  spread(block, include) %>% 
  rename(include1 = `1`, include2 = `2`) %>% 
  mutate(include = case_when(include1 + include2 == 2 ~ 1, include1 + include2 < 2 ~0)) %>% select(-c(include1, include2))

#identify the sub ID of the excluded subs
excludedSubs <- paAccData.sub %>%
  filter(include == 0)
excludedSubIDs = excludedSubs$sub

#Remove excluded subs from paData, subInfo, memData, freqData
subInfo %<>% filter(sub != excludedSubIDs)
memData %<>% filter(sub != excludedSubIDs)
freqData %<>% filter(sub != excludedSubIDs)

#compute mean and sd of included subs
paStats <- paAccData.subBlocks %>% 
  group_by(include) %>%
  summarize(grandMeanPaAcc = mean(meanPaAcc), sdPaAcc = sd(meanPaAcc), minPaAcc = min(meanPaAcc))

#display table
pander(paStats)
```


## Frequency-learning task
```{r compute frequency task accuracy both exps}
#compute accuracy for each trial
freqData %<>% 
  mutate(freqAcc = case_when(freqResp == 0 & freqAppearanceCount == 1 ~ 1, freqResp == 0 & freqAppearanceCount > 1 ~ 0, freqResp == 1 & freqAppearanceCount > 1 ~ 1, freqResp == 1 & freqAppearanceCount == 1 ~ 0))

#combine freqData across experiments
freqDataCombined <- rbind(freqData, freqData_exp2)

#split data based on whether it was the first presentation or repeated presentation
freqDataFirst <- freqDataCombined %>%
  filter(freqAppearanceCount == 1)

freqDataRepeated <- freqDataCombined %>%
  filter(freqAppearanceCount >1)

#for repeated presentation, compute mean accuracy in frequency task for each subject
freqDataSubBlockMeans <- freqDataRepeated %>% 
  group_by(sub, block, age) %>% 
  summarise(N = n(), meanSubAcc = mean(freqAcc, na.rm = TRUE)) %>% 
  arrange(meanSubAcc) %>%
  mutate(badFreqSub = case_when(meanSubAcc < .10 ~ 1, meanSubAcc > .10 ~ 0))

#display table of means
freqDataSubBlockMeans %>% arrange(meanSubAcc)

#merge data frames
freqAccData <- merge(freqDataCombined, freqDataSubBlockMeans, by = c("sub", "block", "age"), all = TRUE)

#remove subjects who performed poorly in the frequency task
freqAccDataFiltered <- freqAccData %>%
  filter(meanSubAcc > .10) %>%
  droplevels()
```



```{r first appearance count freq acc process data both exps}
#set block, subject, item, and exp as factors
freqAccDataFiltered$sub <- as.factor(freqAccDataFiltered$sub)
freqAccDataFiltered$item <- as.factor(freqAccDataFiltered$item)
freqAccDataFiltered$block <- as.factor(freqAccDataFiltered$block)
freqAccDataFiltered$exp <- as.factor(freqAccDataFiltered$exp)

#re-split based on first vs. repeated appearance
freqDataFirst <- freqAccDataFiltered %>%
  filter(freqAppearanceCount == 1)
  
freqDataRepeated <- freqAccDataFiltered %>%
  filter(freqAppearanceCount > 1)
```

### Frequency-learning accuracy
#### Frequency accuracy mixed-effects model: New items
```{r first appearance count freq acc maximal model both exps, eval = F}
freqFirstAppearanceAcc.bothExps.maximal <- mixed(freqAcc ~ block*exp + (block|sub) + (block*exp|item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r first appearance count freq acc 2 both exps}
freqFirstAppearanceAcc.bothExps.2 <- mixed(freqAcc ~ block*exp + (block||sub) + (block*exp||item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(freqFirstAppearanceAcc.bothExps.2)

#return glmer results
freqFirstAppearanceAcc.bothExps.2.glmer <- mixed(freqAcc ~ block*exp + (block||sub) + (block*exp||item), data = freqDataFirst, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(freqFirstAppearanceAcc.bothExps.2.glmer)
```

#### Frequency accuracy mixed-effects model: Repeated items
```{r first appearance count freq acc scale variables both exps}
freqDataRepeated$appearanceCountScaled <- scale_this(freqDataRepeated$freqAppearanceCount)
```

```{r freq acc maximal model both exps, eval = F}
freqAcc.bothExps.maximal <- mixed(freqAcc ~  block * appearanceCountScaled *exp + (block* appearanceCountScaled|sub) + (block * appearanceCountScaled * exp|item), data = freqDataRepeated, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r freq acc  model 2 both exps}
freqAcc.bothExps.2 <- mixed(freqAcc ~  block * appearanceCountScaled *exp + (block* appearanceCountScaled||sub) + (block * appearanceCountScaled * exp||item), data = freqDataRepeated, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

#display
nice(freqAcc.bothExps.2)

#return glmer object
freqAcc.bothExps.2.glmer <- mixed(freqAcc ~  block * appearanceCountScaled *exp + (block* appearanceCountScaled||sub) + (block * appearanceCountScaled * exp||item), data = freqDataRepeated, family = binomial, method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

#display
summ(freqAcc.bothExps.2.glmer)
```


#### Plot: Frequency task accuracy
```{r freqAcc interaction plot both exps}
freqAccPlotData <- freqAccData %>% 
  group_by(freqAppearanceCount, exp, block) %>% 
  summarise(meanFreqAcc = mean(freqAcc, na.rm = T), sdFreqAcc = sd(freqAcc, na.rm = T), N = n(), seAcc = sdFreqAcc/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanFreqAcc + seAcc, ymin = meanFreqAcc - seAcc)

#make plot
freqAccPlot <- ggplot(freqAccPlotData, aes(x = freqAppearanceCount, y = meanFreqAcc, fill = block)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(errorBars, position = position_dodge(width = .9), width = .1) +
  xlab("Appearance Count") +
  ylab("Frequency Task Accuracy") +
  #ggtitle("Frequency Task Reaction Times") + 
  scale_fill_manual(values = c(color1, color3)) +
  facet_wrap(~exp) +
  kate.theme
freqAccPlot
```


### Frequency task reaction times
```{r frequency task RT data processing both exps}
#Filter out inaccurate trials
freqRTdata <-freqDataRepeated %>%
  filter(freqAcc == 1)

#scale appearance count
freqRTdata$appearanceCountScaled <- scale_this(freqRTdata$appearanceCount)
```

#### Frequency task reaction times mixed-effects model
```{r frequency task RT maximal model both exps, eval = F}
freqRT.bothExps.maximal <- mixed(freqRT ~  appearanceCountScaled * block * exp + (appearanceCountScaled * block|sub) + (appearanceCountScaled * block * exp|item), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r frequency task RT model 2 both exps}
#remove correlations
freqRT.bothExps.2 <- mixed(freqRT ~  appearanceCountScaled * block * exp + (appearanceCountScaled * block||sub) + (appearanceCountScaled * block * exp||item), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(freqRT.bothExps.2)

#display lmer results
freqRT.bothExps.2.lmer <- mixed(freqRT ~  appearanceCountScaled * block * exp + (appearanceCountScaled * block||sub) + (appearanceCountScaled * block * exp||item), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(freqRT.bothExps.2.lmer)
```


#### Plot: Frequency task reaction times
```{r freqRT interaction plot both exps}
freqRTPlotData <- freqRTdata %>% 
  group_by(freqAppearanceCount, exp) %>% 
  summarise(meanFreqRT = mean(freqRT, na.rm = T), sdFreqRT = sd(freqRT, na.rm = T), N = n(), seRT = sdFreqRT/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanFreqRT + seRT, ymin = meanFreqRT - seRT)

#make plot
freqRTPlot <- ggplot(freqRTPlotData, aes(x = freqAppearanceCount, y = meanFreqRT, fill = exp)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(errorBars, position = position_dodge(width = .9), width = .1) +
  xlab("Appearance Count") +
  ylab("Frequency Task Reaction Times (s)") +
  ggtitle("Frequency Task Reaction Times") + 
  scale_fill_manual(values = c(color1, color3)) +
  kate.theme
freqRTPlot
```


## Explicit frequency reports
```{r compute freq response error both exps}
#remove columns from memData that are not in the memData_exp2 data frame
memData %<>% select(-c(stimNum, memAppearanceCount))

#compute response error and response error magnitude
memData %<>% mutate(memFreqRespError = memFreqResp - as.numeric(as.character(freqCond)), memFreqRespErrorMagnitude = abs(memFreqRespError))

#remove columns from memData_exp2 that are not in the memData data frame
memData_exp2 %<>% select(-c(memAcc, memFreqRespScaled))

#combine them
memDataCombined <-  bind_rows(memData, memData_exp2)

#code frequency condition, block, subject, item, and experiment as factors
memDataCombined$freqCondFactor <- as.factor(memDataCombined$freqCond)
memDataCombined$exp <- as.factor(memDataCombined$exp)
memDataCombined$sub <- as.factor(memDataCombined$sub)
memDataCombined$block <- as.factor(memDataCombined$block)
memDataCombined$item <- as.factor(memDataCombined$item)
```

### Frequency error mixed-effects model
```{r explicit freq error maximal model both exps, eval = F}
freqError.bothExps.maximal <- mixed(memFreqRespErrorMagnitude ~ freqCondFactor *exp *block+ (freqCondFactor*block|sub) + (freqCondFactor *exp *block|item), data = memDataCombined, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r explicit freq error model 2 both exps}
#remove correlations
freqError.bothExps.2 <- mixed(memFreqRespErrorMagnitude ~ freqCondFactor *exp *block+ (freqCondFactor*block||sub) + (freqCondFactor *exp *block||item), data = memDataCombined, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(freqError.bothExps.2)

#display lmer results
freqError.bothExps.2.lmer <- mixed(memFreqRespErrorMagnitude ~ freqCondFactor *exp *block+ (freqCondFactor*block||sub) + (freqCondFactor *exp *block||item), data = memDataCombined, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(freqError.bothExps.2.lmer)
```


### Plot: Frequency report distributions
```{r frequency histograms both exps}
#plot histogram of frequency responses as a function of frequency
meanFreqResp <- memDataCombined %>% 
  group_by(freqCond, exp) %>% 
  summarise(meanFreqResp = mean(memFreqResp, na.rm = TRUE))

#make plot
freqRespHist <- ggplot(memDataCombined, aes(x = (memFreqResp), color = freqCondFactor, fill = freqCondFactor)) +
  facet_wrap(~exp) +
  stat_count(position = "identity", alpha = .5) +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_color_manual(values = c(color1, color3), name = "Frequency Condition") + 
  xlab("Reported Frequency") +
  ylab("Number of Responses") +
   scale_x_discrete(limits = c(1:10)) +
  ggtitle("Adults") +
  kate.theme 
freqRespHist
```


## Memory test
```{r compute memory accuracy both exps}
#compute memory accuracy for each trial
memDataCombined %<>%
  mutate(memAcc = case_when(as.character(memResp) == as.character(gridLocation) ~ 1,
                            as.character(memResp) != as.character(gridLocation) ~ 0))
                            
```

### Memory accuracy mixed-effects model
```{r memory accuracy maximal model both exps, eval = F}
memAcc.bothExps.maximal <- mixed(memAcc ~  freqCondFactor * block *exp + (freqCondFactor*block|sub) + (freqCondFactor*block*exp|item), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r memory accuracy model 2 both exps}
memAcc.bothExps.2 <- mixed(memAcc ~  freqCondFactor * block *exp + (freqCondFactor*block||sub) + (freqCondFactor*block*exp||item), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(memAcc.bothExps.2)

#display glmer results
memAcc.bothExps.2.glmer <- mixed(memAcc ~  freqCondFactor * block *exp + (freqCondFactor*block||sub) + (freqCondFactor*block*exp||item), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(memAcc.bothExps.2.glmer)
```

### Plot: Effects of frequency condition and block on memory
```{r memory accuracy plot both exps, fig.width = 10, fig.height = 6}
memPlotData <- memDataCombined %>% 
  group_by(freqCondFactor, block, exp) %>% 
  summarise(meanAcc = mean(memAcc, na.rm = T), sdAcc = sd(memAcc, na.rm = T), N = n(), seAcc = sdAcc/sqrt(N))

#compute error bar limits
errorBars <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

memAccPlot <- ggplot(memPlotData, aes(x = block, fill = freqCondFactor, y = meanAcc)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(errorBars, position = position_dodge(width = .9), width = .1) +
  facet_wrap(~ exp) +
  coord_cartesian(ylim = c(0, .75)) +
  xlab("Experiment Block") +
  ylab("Memory Accuracy") +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  ggtitle("Memory Accuracy") + 
  kate.theme
memAccPlot

```

### Plot: Effects of frequency condition on memory (individual subjects)
```{r memory accuracy plot 2 both exps, fig.width = 10, fig.height = 6}
memPlotData <- memDataCombined %>% 
  group_by(sub, freqCondFactor, exp, block) %>% 
  summarise(meanAcc = mean(memAcc, na.rm = T), sdAcc = sd(memAcc, na.rm = T), N = n(), seAcc = sdAcc/sqrt(N)) %>%
  mutate(Experiment = case_when(exp == 1 ~ "Experiment 1", exp == 2 ~ "Experiment 2"))

#compute error bar limits
errorBars <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

memAccPlotSub <- ggplot(memPlotData, aes(x = block, y = meanAcc, fill = freqCondFactor)) +
  facet_wrap(~ Experiment) +
  geom_boxplot(position = position_dodge(.8), alpha = .8) +
  geom_hline(yintercept = .05, linetype = "dashed") +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  stat_summary(fun.y = mean, geom = "point",
               shape = 4, size = 2.5, color = "white", position = position_dodge(.8)) +
  coord_cartesian(ylim = c(0, 1)) +
  xlab("Block") +
  ylab("Memory Accuracy") +
  #ggtitle("Memory Accuracy") + 
  kate.theme
memAccPlotSub

ggsave("memAccBothExps.png", width = 8, height = 4, units = "in", dpi = 1000)
```


## Relation between learning environmental statistics and memory encoding
```{r memory and frequency indices both exps}
#create memory benefit index as specified in the pre-registration
  #first compute each subject's average memory performance in the 1 and 5 condition
temp <- memDataCombined %>% 
  group_by(sub, freqCond, block, age, IQ, exp) %>% 
  summarise(meanMem = mean(memAcc, na.rm = TRUE))
  
#make frequency condition a column in the table and then compute difference
temp <- spread(temp, freqCond, meanMem) %>%
  mutate(memDiff = `5` - `1`)

  #compute overall memory accuracy
temp2 <- memDataCombined %>% 
  group_by(sub, block, age) %>% 
  summarise(overallMeanMem = mean(memAcc, na.rm = TRUE))

  #merge data frames and compute memBenefitIndex
memBenefit <- full_join(temp, temp2, by = c("sub", "block", "age")) %>% 
  mutate(memBenefitIndex = memDiff / overallMeanMem) %>% 
  select(-c(`5`, `1`, memDiff, overallMeanMem))

#create frequency distance index  as specified in the pre-registration

  #compute mean z score per frequency condition
meanZs <- memDataCombined %>% 
  group_by(sub, block, freqCond, age, IQ) %>% 
  summarise(meanFreqRespZ = mean(freqRespZ, na.rm = TRUE))
  
  #spread data
freqDist <- spread(meanZs, freqCond, meanFreqRespZ) %>% 
  mutate(freqDist = `5` - `1`) %>% 
  select(-c(`5`, `1`))

#combine with mem benefit index
subIndices <- merge(memBenefit, freqDist, by = c("sub", "block", "age", "IQ"))

#remove rows where memBenfit is NaN
subIndices %<>%
  filter(!is.na(memBenefitIndex))

#scale age, IQ, and frequency distance
subIndices$freqDistScaled <- scale_this(subIndices$freqDist)

```

### Memory benefit mixed-effects model
```{r memory benefit by frequency index model both exps}
memBenefit.bothExps.model <- mixed(memBenefitIndex ~ freqDistScaled *block *exp  + (1|sub), data = subIndices, method = "KR", control = lmerControl(optCtrl=list(maxfun=1e6)))

nice(memBenefit.bothExps.model)

#display lmer results
memBenefit.bothExps.model.lmer <- mixed(memBenefitIndex ~ freqDistScaled *block *exp  + (1|sub), data = subIndices, method = "KR", control = lmerControl(optCtrl=list(maxfun=1e6)), return = "merMod")

summ(memBenefit.bothExps.model.lmer)
```

### Plot: Relation between frequency distance and memory benefit
```{r frequency distance memory benefit plot both exps}
freqDistMemBenefitPlot <- ggplot(subIndices, aes(x = freqDist, y = memBenefitIndex), color = color3, fill = color3) +
  geom_point(color = color3) +
  geom_smooth(method = "lm", color = color3, fill = color3) +
  facet_wrap(~exp) +
  xlab("Frequency Distance") +
  ylab("Memory Benefit Index") +
  kate.theme
freqDistMemBenefitPlot
```

### Item-level relation between frequency reports and memory mixed-effects model
```{r item-level freq reports and memory data processing both exps}
#scale frequency reports
memDataCombined$memFreqRespScaled <- scale_this(memDataCombined$memFreqResp)
```

```{r mem freq relation model both exps, eval = F}
memFreqRelation.bothExps.maximal <- mixed(memAcc ~ memFreqRespScaled * block *exp + (memFreqRespScaled * block|sub) + (memFreqRespScaled * block * exp|item),data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

#does not converge
```

```{r mem freq relation model 2 both exps}
memFreqRelation.bothExps.2 <- mixed(memAcc ~ memFreqRespScaled * block *exp + (memFreqRespScaled * block||sub) + (memFreqRespScaled * block * exp||item), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T)

nice(memFreqRelation.bothExps.2)

#display glmer results
memFreqRelation.bothExps.2.glmer <- mixed(memAcc ~ memFreqRespScaled * block *exp + (memFreqRespScaled * block||sub) + (memFreqRespScaled * block * exp||item), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), expand_re = T, return = "merMod")

summ(memFreqRelation.bothExps.2.glmer)
```


### Plot: Effects of frequency report on memory accuracy
```{r plot memory by explicit frequency (1) both exps, fig.align = "center", fig.width = 7, fig.height = 4}
#plot memory by explicit frequency
memByExplicitFreq1 <- memDataCombined %>%
  filter(memFreqResp > 0 & freqCond == 1) %>%
  group_by(memFreqResp, freqCond, exp) %>% 
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N))) 

memByExplicitFreq5 <- memDataCombined %>%
  filter(memFreqResp > 0 & freqCond == 5) %>%
  group_by(memFreqResp, freqCond, exp) %>% 
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N))) 

accLimits <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color1
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot1 <- ggplot(memByExplicitFreq1, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color1) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color1) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color1) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  facet_wrap(~ exp) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  ggtitle("1-Frequency Condition") +
  NULL
explicitFreqMemPlot1
```

```{r plot memory by explicit frequency (5) both exps, fig.align = "center", fig.width = 7, fig.height = 4}
#Repeat for 5 frequency condition

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color3
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot5 <- ggplot(memByExplicitFreq5, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color3) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color3) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color3) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  facet_wrap(~ exp) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  ggtitle("5-Frequency Condition") +
  NULL
explicitFreqMemPlot5

```

```{r plot memory by explicit frequency both exps, fig.align = "center", fig.width = 7, fig.height = 4}
#Both frequency conditions together
memByExplicitFreqCombined <- memDataCombined %>% 
  filter(memFreqResp > 0) %>%
  group_by(memFreqResp, exp) %>% 
  summarise(meanAcc = mean(memAcc), sdAcc= sd(memAcc), N = n(),seAcc = sdAcc/(sqrt(N)))  %>%
  mutate(Experiment = case_when(exp == 1 ~ "Experiment 1", exp == 2 ~ "Experiment 2"))

accLimits <- aes(ymax = meanAcc + seAcc, ymin = meanAcc - seAcc)

#do stuff to make alpha legend continuous
amin <- 0.1
highcol <- color2
lowcol.hex <- as.hexmode(round(col2rgb(highcol) * amin + 255 * (1 - amin)))
lowcol <- paste0("#",   sep = "",
                 paste(format(lowcol.hex, width = 2), collapse = ""))

explicitFreqMemPlot <- ggplot(memByExplicitFreqCombined, aes(x = memFreqResp, y = meanAcc, alpha = N), color = color2) +
  geom_bar(stat = "identity", position = "dodge", fill = highcol, size = .4, color = color2) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0, aes(fill = N), color = color2) +
  scale_fill_gradient(high = highcol, low = lowcol, name = "Number of Trials", guide = guide_colorbar(frame.colour = "black", ticks.colour = "black")) +
 geom_errorbar(accLimits, position = position_dodge(width = .9), width = .2, color = "black", alpha = 1) +
  facet_wrap(~ Experiment) +
  kate.theme +
  theme(strip.background = element_blank()) +
  theme(legend.position = "right", legend.text=element_text(size=12), legend.title = element_text(size = 12)) +
  scale_x_discrete(limits = c("1","2","3","4","5","6","7","8","9","10"), breaks = c(1,5,10), labels = c("1", "5", "10")) +
  guides(alpha = F) + 
  labs(fill = "Alpha\nlabel") +
  xlab("Explicit Frequency Report") + ylab ("Memory Accuracy") +
  #ggtitle("Both Frequency Conditions") +
  NULL
explicitFreqMemPlot

#ggsave("explicitFreqMemPlot.png", width = 8, height = 4, units = "in", dpi = 1000)
```