---
title: 'Supplementary Material: Experiment S1'
author: "Kate Nussenbaum"
date: "11/20/18"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

<style type="text/css">

h1.title {
  font-size: 38px;
}
h1 { /* Header 1 */
  font-size: 28px;
}
h2 { /* Header 2 */
    font-size: 22px;
}
h3 { /* Header 3 */
  font-size: 18px;
}

</style>


```{r, setup, include = FALSE}
knitr:: opts_chunk$set(cache = TRUE, echo = FALSE, warning = FALSE, message = FALSE)
knitr:: opts_chunk$set(out.width='500px', out.height = '300px', dpi=1000, fig.align='center')
```

```{r libraries and paths}
## SECTION 0: Set everything up
#First we will load the libraries we are going to use for our analysis.
# Load needed libraries
library(tidyverse)
library(magrittr)
library(pander)
library(readxl)
library(afex)
library(sjPlot)
library(sjmisc)
library(lmSupport)

#Set path to data
dataFolder <- "supplement_data/"

```

```{r create ggplot theme}
#create standard themes to use for ggplot
kate.theme <- theme(panel.background = element_rect(fill='transparent'),
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        axis.title.x = element_text(size=14, vjust=-.25),
                        axis.title.y = element_text(size=14, vjust=1),
                        axis.text.x = element_text(size=12, colour="black"),
                        axis.text.y = element_text(size=12, colour="black"),
                        legend.text=element_text(size=12),
                        legend.title = element_text(size = 14),
                        plot.title = element_text(size=16, face = "bold", hjust = .5))


#Define 3 theme colors to use
color1 = "#78C2C3"
color2 = "#3F6699"
color3 = "#0D1B4C"
```

```{r scale function}
#define new function so that scale returns a vector, not a matrix
scale_this <- function(x) as.vector(scale(x))
```

```{r import data}
## IMPORT SUBJECT INFORMATION ##

# Read in file that contains the subject information
subInfo <- read_excel(paste(dataFolder,"subInformation_S1.xlsx", sep= ""), sheet = 1)
subInfo <- data.frame(subInfo)   

#Change ID and strategy variables from integers to factors
subInfo$ID <- as.factor(subInfo$ID)
subInfo$GeneratedStrategy<- as.factor(subInfo$GeneratedStrategy)
  #Note: Level 1 of strategy variables now corresponds to "1" - the subject DID generate  the strategy
  # Level 2 of strategy variables correspond to "0" - the subject DID NOT generate the strategy

## IMPORT TASK DATA ##
# Create two empty data frames
  memDF <- data.frame() 
  freqDF <- data.frame()

##### Read in each subject's data #####
for (i in 1:nrow(subInfo)) {
   
    #define names of files
    sub <- subInfo$ID[i]
    freq_filename <- paste(dataFolder, paste(sub, "_freqTask.txt", sep = ""), sep = "")
    PA_filename <- paste(dataFolder, paste(sub, "_PA.txt", sep = ""), sep = "") 
    memGrid_filename <- paste(dataFolder, paste(sub,"_memTestFoodGrid.txt", sep = ""), sep = "") 
    memTest_filename <- paste(dataFolder, paste(sub,"_mem.txt", sep = ""), sep = "") 
    
    #read in files for each subject & add column with their subject numbers
    freq_data  <- read.delim(text = gsub("\\t$", "", readLines(freq_filename)), header = FALSE) 
    freq_data$ID <- sub
    PA_data  <- read.delim(text = gsub("\\t$", "", readLines(PA_filename)), header = FALSE)
    PA_data$ID <- sub
    memGrid_data  <- read.delim(text = gsub("\\t$", "", readLines(memGrid_filename)), header = FALSE)
    memTest_data  <- read.delim(text = gsub("\\t$", "", readLines(memTest_filename)), header = FALSE)
    
  # add variable names to columns, eliminate unnecessary columns, make sure all the variable types are correct
    freq_data %<>% rename(animal = V1, freqCond = V2, freqResp = V3, freqRT = V4, freqTrial = V7) %>% select(-starts_with("V")) 
    PA_data %<>% rename(paFood = V1, animal = V2, foodSide = V3, paResp = V4, paRT = V5, paTrial = V8) %>% select(-starts_with("V")) 
    memGrid_data %<>% rename(paFood = V1, memGridLocation = V2)
    memTest_data %<>% rename(animal = V1, memRT = V4, memResp = V5) %>% select(-starts_with("V"))

  #add column to frequency data frame that counts the number of times the animal has appeared
    freq_data$appearanceCount <- 1 #set the appearanceCount to 1
    for (i in 2:nrow(freq_data)){
      for (j in 1:(i-1)){
        if (freq_data$animal[i] == freq_data$animal[j]){
          freq_data$appearanceCount[i] <- freq_data$appearanceCount[i] + 1
        }}}
    
  #add column to memory test data frame that counts the number of times the animal has appeared
    memTest_data$memAppearanceCount <- 1 #set the appearanceCount to 1
    for (i in 2:nrow(memTest_data)){
      for (j in 1:(i-1)){
        if (memTest_data$animal[i] == memTest_data$animal[j]){
          memTest_data$memAppearanceCount[i] <- memTest_data$memAppearanceCount[i] + 1
        }}}
    
    #merge the memory test data with the paired associates data
    memData <-  merge(memTest_data, PA_data, by = "animal", all = TRUE)
    
    #add in information about where the foods were in each grid
    memData <- merge(memData, memGrid_data, by = "paFood", all = TRUE)
    
    #create a new data frame that has the frequency condition for each animal by taking the average frequency (since all the frequencies for each animal will be the same, this is just like extracting a row)
    animalFrequencies <- group_by(freq_data, animal) %>%
    summarize(freqCond = mean(freqCond))
    
    #merge this with the memory data
    memData <- merge(memData, animalFrequencies, by = "animal")
    
    # Now for each subject, there are two data frames: 
    # memData: Contains all the info needed for the analysis of the PA task and the memory test 
    # freq_data: Contains all the info needed for the analysis of the frequency task
    
  #### Merge all subject data together ####
  memDF <- bind_rows(memDF, memData)
  freqDF <- bind_rows(freqDF, freq_data)
}
  
# merge data with subject info
memDataCombined <- full_join(memDF, subInfo, by = "ID")
freqDataCombined <- merge(freqDF, subInfo, by = "ID")

#make sure all columns are the correct type
memDataCombined %<>% mutate_at(c("animal", "paFood", "memResp", "ID", "memGridLocation", "GeneratedStrategy"), funs(as.factor(.)))

freqDataCombined %<>% mutate_at(c("ID", "animal", "freqResp", "GeneratedStrategy"), funs(as.factor(.)))

#restrict mem data to the first appearance of each item
memDataAll <- memDataCombined #save a data frame with ALL memory trials
memDataCombined <- memDataCombined[which(memDataCombined$memAppearanceCount ==1),] #create a data frame just with the memory trials of interest
```


```{r paired associates exclusion}
## EXCLUDE SUBJECTS WHO PERFORMED BELOW-CHANCE (50%) ON PAIRED-ASSOCIATES TASK ##

#Combine all the repeated rows that refer to the same trial in the PA task
pa_data <- memDataCombined %>% group_by(ID, paTrial, foodSide) %>% summarize(paResp = mean(paResp, na.rm = TRUE))

#convert food side to numeric
pa_data$foodSide <- as.numeric(as.character(pa_data$foodSide))

#Compute PA accuracy for each trial for each subject
pa_data <- pa_data %>% mutate(acc = case_when(paResp - foodSide == 0 ~ 1, paResp - foodSide != 0 ~ 0))

#Compute PA accuracy for each subject
paAccData.sub <- pa_data %>% group_by(ID) %>% summarize(meanPaAcc = mean(acc)) %>% mutate(include = case_when(meanPaAcc > .66 ~ 1, meanPaAcc <.667 ~ 0))

#exclude subs from subInfo, memData frame, freqData frame
subInfo <- merge(subInfo, paAccData.sub, by = "ID", all = T)
subInfo <- subInfo[which(subInfo$include ==1),]
subInfo$ID <- factor(subInfo$ID)
memDataCombined <- merge(memDataCombined, paAccData.sub, by = c("ID"), all = T)
memDataCombined <- memDataCombined[which(memDataCombined$include == 1),]
memDataCombined$ID <- factor(memDataCombined$ID)
freqDataCombined <- merge(freqDataCombined, paAccData.sub, by = c("ID"), all = T)
freqDataCombined <- freqDataCombined[which(freqDataCombined$include == 1),]
freqDataCombined$ID <- factor(freqDataCombined$ID)
```

```{r compute structural learning index}
## COMPUTE STRUCTURAL LEARNING INDEX ##
#First compute frequency accuracy
#Make a variable to specify what the response should be 
freqDataCombined$correctResp <- ifelse(freqDataCombined$appearanceCount > 1, 1, 0)

#Then compute whether the participant made the right response
freqDataCombined$acc <- ifelse(freqDataCombined$freqResp == freqDataCombined$correctResp, 1, 0)

#Get the mean RT for each subject for each appearance of the stimulus during the frequency task
meanFreqRTs <- freqDataCombined %>%
  group_by(ID, appearanceCount) %>% summarize(meanFreqRT = mean(freqRT, na.rm = TRUE))

overallMeanFreqRT <- freqDataCombined %>%
  group_by(ID) %>% summarize(meanFreqRT = mean(freqRT, na.rm = TRUE), sdFreqRT = sd(freqRT, na.rm = T))

# compute learning index by subtracting 6RT from 2RT and dividing by mean RT, then get rid of unnecessary columns and merge learning index with the memory data frame
temp1 <- meanFreqRTs %>% spread(appearanceCount, meanFreqRT)
temp1 <- full_join(temp1, overallMeanFreqRT, by = "ID")
temp1 <- temp1 %>% rename(six = '6', five = '5', four = '4', three = '3', two = '2', one = '1') %>% mutate(learningIndex = (two - six)/sdFreqRT) %>% select(-c(one, two, three, four, five, six, meanFreqRT, sdFreqRT))
temp1$ID <- as.factor(temp1$ID)

memDataCombined <- full_join(memDataCombined, temp1, by = "ID")
```

```{r compute memory benefit index}

# Compute memory accuracy. NOTE: Trials in which the participant failed to respond will be coded as NA
memDataCombined$memAcc <- ifelse(as.character(memDataCombined$memResp) == as.character(memDataCombined$memGridLocation), 1, 0)

#make frequency condition grouping variable
memDataCombined$freqCondFactor <- as.factor(memDataCombined$freqCond)

#get the mean memory accuracy score for each subject for each frequency condition
meanMemAcc <- memDataCombined %>%
  group_by(ID, freqCondFactor) %>% summarize(meanMemAcc = mean(memAcc, na.rm = TRUE))

#get the overall mean memory accuracy score
overallMeanMemAcc<- memDataCombined %>%
  group_by(ID) %>% summarize(meanMemAcc = mean(memAcc, na.rm = TRUE))

# compute memory benefit index by subtracting 1acc from 6acc and dividing by mean acc, then get rid of unnecessary columns and merge the memory benefit index data frame with the memory data frame
temp1 <- meanMemAcc %>% spread(freqCondFactor, meanMemAcc)
temp1 <- full_join(temp1, overallMeanMemAcc, by = "ID")
temp1 <- temp1 %>% rename(six = '6', three = '3', one = '1') %>% mutate(memBenefitIndex = (six - one)/meanMemAcc) %>% select(-c(one, three,  six, meanMemAcc))

memDataCombined <- full_join(memDataCombined, temp1, by = "ID")
```

```{r split age groups}
# SPLIT DAT INTO AGE GROUPS (for plotting purposes only)
memDataCombined <- memDataCombined  %>% mutate(ageGroup = case_when(Age < 13 ~ "Child", Age > 13 & Age < 18 ~ "Adolescent", Age > 18 ~ "Adult"))

freqDataCombined <- freqDataCombined %>% mutate(ageGroup = case_when(Age < 13 ~ "Child", Age > 13 & Age < 18 ~ "Adolescent", Age > 18 ~ "Adult"))

#set as factors and specify factor order
memDataCombined$ageGroup <- factor(memDataCombined$ageGroup, levels = c("Child", "Adolescent", "Adult"))
freqDataCombined$ageGroup <- factor(freqDataCombined$ageGroup, levels = c("Child", "Adolescent", "Adult"))
```


# Subject statistics
First, we will determine whether IQ correlates with age in our sample. As specified in our pre-registration, here we run run a linear regression testing the effects of age on IQ. 

```{r IQ age regression and plot}
# Run linear regression testing the effects of age on IQ
ageIQ.lm <- lm(IQ ~ Age, data = subInfo) #run regression
ageIQeffectSize <- modelEffectSizes(ageIQ.lm, Print = F, Digits = 3)
ageIQsummary <-(anova(ageIQ.lm))
ageIQsummary$pEta[1] <-ageIQeffectSize$Effects[2,3]
ageIQsummary$pEta[2] <-NA
pander(ageIQsummary)

# Plot the correlations
ageIQPlot <- ggplot(subInfo, aes(x = Age, y = IQ)) +
  geom_point() +
  stat_smooth(method = "lm", color = color2) + 
  xlab("Age") + ylab ("IQ") +
kate.theme
ageIQPlot

```
This analysis indicates that there is a significant relation between age and IQ. As such, we will run all subsequent models both with and without IQ as an interacting fixed effect to better tease apart effects of age from effects of IQ.


# Frequency task analysis
_In this section, we will run mixed effects models to determine the effects of appearance count and age on participants' accuracy and reaction time during the frequency task. For both models, we will start with the maximal random effects structure. If the models do not converge, we will remove random slopes and intercepts as specified in the pre-registration. As we preregistered, if the maximal model does not converge, we will follow the procedure laid out in Singmann & Kellen (2017) to reach convergence. They recommend first removing correlations between random slopes and random intercepts. If models stil fail to converge, they recommend removing random-effects parameters 'starting with the highest-order random effects parameter with the lowest estimated variance._

## Frequency task accuracy
First, we will ensure that all subjects responded to >10% of repeated trials, indicating that they understood the task instructions.
```{r divide freq accuracy data by old and new}
#Divide frequency data into new items and old items
freqDataRepeatedItems <- freqDataCombined[which(freqDataCombined$appearanceCount > 1),]
freqDataNewItems <- freqDataCombined[which(freqDataCombined$appearanceCount == 1),]

#compute each subjects' accuracy
freqDataSubAcc <- freqDataRepeatedItems %>% group_by(ID) %>% summarise(meanFreqAcc = mean(acc, na.rm = TRUE)) %>% arrange(meanFreqAcc)

#print data frame to ensure all subjects responded with a reasonably high degree of accuracy
freqDataSubAcc

#scale continuous variables used in models
freqDataRepeatedItems %<>% mutate(ageScaled = scale_this(Age), appearanceCountScaled = scale_this(appearanceCount), IQScaled = scale_this(IQ))

freqDataNewItems %<>% mutate(ageScaled = scale_this(Age), IQScaled = scale_this(IQ))
```


## Frequency accuracy mixed-effects model: New items without IQ
```{r frequency accuracy new item model no IQ maximal}
#Run maximal mixed effects model examining the effects of appearance count on participant accuracy
freqAccModel.newItems.maximal <- mixed(acc ~ ageScaled + (1|ID) + (ageScaled|animal), data = freqDataNewItems, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqAccModel.newItems.maximal
```

## Frequency accuracy mixed-effects model: New items with IQ
```{r frequency accuracy new item model with IQ maximal}
#Run maximal mixed effects model examining the effects of appearance count on participant accuracy (no correlations)
freqAccModel.IQ.newItems.maximal <- mixed(acc ~ ageScaled * IQScaled + (1|ID) + (ageScaled *IQScaled|animal), data = freqDataNewItems, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqAccModel.IQ.newItems.maximal
```


## Frequency accuracy: Repeated items without IQ
```{r frequency accuracy old item model no IQ}
#Run maximal mixed effects model examining the effects of appearance count on participant accuracy
freqAccModel.oldItems <- mixed(acc ~ ageScaled *appearanceCountScaled + (appearanceCountScaled|ID) + (ageScaled*appearanceCountScaled|animal), data = freqDataRepeatedItems, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqAccModel.oldItems
```

## Frequency accuracy: Repeated items with IQ
```{r frequency accuracy old item model with IQ}
#Run maximal mixed effects model examining the effects of appearance count on participant accuracy
freqAccModel.IQ.oldItems <- mixed(acc ~ ageScaled * IQScaled *appearanceCountScaled + (appearanceCountScaled|ID) + (ageScaled *IQScaled*appearanceCountScaled|animal), data = freqDataRepeatedItems, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqAccModel.IQ.oldItems
```


## Frequency accuracy: Plot
```{r frequency accuracy effects plots}
#first compute means of each condition
freqAccMeans <- freqDataRepeatedItems %>% group_by(appearanceCount, ageGroup) %>% summarize(meanFreqAcc = mean(acc), sdFreqAcc = sd(acc), N = n(), seFreqAcc = sdFreqAcc/sqrt(N), min = meanFreqAcc - seFreqAcc, max = meanFreqAcc + seFreqAcc)

freqAccPlot.age <- ggplot(freqAccMeans, aes(x = appearanceCount, y = meanFreqAcc, fill = ageGroup)) +
  geom_point(stat = "identity", aes(color = ageGroup), size = 2, show.legend = F) +
  geom_line(stat = "identity", aes(color = ageGroup), size = 1.5) +
  geom_errorbar(data = freqAccMeans, aes(x = appearanceCount, ymin = min, ymax = max, color = ageGroup), width = .2, stat = "identity") +
  coord_cartesian(ylim = c(.85, 1)) + 
  xlab("Appearance Count") +
  ylab("Proportion Correct") +
  scale_color_manual(values=c(color1, color2, color3)) +
  ggtitle("Frequency Task Accuracy") + 
  guides(color = guide_legend(title = "Age Group")) + 
  kate.theme
freqAccPlot.age 
```

## Frequency task reaction times: Repeated items without IQ
```{r freq RT data processing}
#first, create new data frame with correct trials only, as was specified in the pre-registration
freqRTdata <- freqDataRepeatedItems[which(freqDataRepeatedItems$acc == 1),]

#rescale age, appearance count and IQ
freqRTdata$ageScaled <- scale_this(freqRTdata$Age)
freqRTdata$appearanceCountScaled <- scale_this(freqRTdata$appearanceCount)
freqRTdata$IQScaled <- scale_this(freqRTdata$IQ)
```

```{r freq RT mixed model no IQ}
#Run maximal mixed effects model examining the effects of appearance count on participant RT
freqRTModel <- mixed(freqRT ~ appearanceCountScaled*ageScaled + (appearanceCountScaled|ID) + (appearanceCountScaled*ageScaled|animal), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqRTModel
```

## Frequency task reaction times: Repeated items with IQ
```{r freq RT mixed model}
#Run maximal mixed effects model examining the effects of appearance count on participant RT
freqRTModel.IQ <- mixed(freqRT ~ appearanceCountScaled*ageScaled*IQScaled + (appearanceCountScaled|ID) + (appearanceCountScaled*ageScaled*IQScaled|animal), data = freqRTdata, method = "KR", control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

freqRTModel.IQ
```

## Frequency task reaction times: Plot
```{r frequency RT effects plots}
#first compute means of each condition
freqRTMeans <- freqRTdata %>% group_by(appearanceCount, ageGroup) %>% summarize(meanFreqRT = mean(freqRT), sdFreqRT = sd(freqRT), N = n(), seFreqRT = sdFreqRT/sqrt(N), min = meanFreqRT - seFreqRT, max = meanFreqRT + seFreqRT)

freqRTPlot.age <- ggplot(freqRTMeans, aes(x = appearanceCount, y = meanFreqRT, fill = ageGroup)) +
  geom_line(stat = "identity", aes(color = ageGroup), size = 1.5) +
  geom_point(stat = "identity", aes(color = ageGroup), size = 2, show.legend = F) +
  geom_errorbar(data = freqRTMeans, aes(x = appearanceCount, ymin = min, ymax = max, color = ageGroup), width = .2, stat = "identity") +
  coord_cartesian(ylim = c(.5, 1)) + 
  xlab("Appearance Count") +
  ylab("RT (seconds)") +
  scale_color_manual(values=c(color1, color2, color3)) +
  ggtitle("Frequency Task Reaction Times") + 
  guides(color = guide_legend(title = "Age Group")) + 
  kate.theme
freqRTPlot.age 
```


#Memory test analysis

_In this section, we will run four mixed effects models to examine the effects of frequency condition on memory accuracy (both with and without IQ included). We will deviate from our pre-registration by only analyzing the data from the first appearance of each item during the memory test (the first 30 trials). We will follow the same procedure as with our frequency data to find the maximal random effects structure that converges._

## Memory accuracy without IQ

```{r memory acc data processing, echo = F}

#rescale age, frequency and IQ
memDataCombined$ageScaled <- scale_this(memDataCombined$Age)
memDataCombined$freqCondScaled <- scale_this(memDataCombined$freqCond)
memDataCombined$IQScaled <- scale_this(memDataCombined$IQ)
```

```{r memory acc first appearance model, eval = F}
#maximal model
memAccModel <- mixed(memAcc ~ freqCondScaled * ageScaled  + (freqCondScaled|ID) + (freqCondScaled*ageScaled|animal), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

memAccModel

#THIS MODEL PRODUCES CONVERGENCE ERRORS
```

```{r memory acc first appearance no correlations}
#Remove correlations between random slopes and intercepts
memAccModel.2 <- mixed(memAcc ~ freqCondScaled * ageScaled   + (freqCondScaled||ID) + (freqCondScaled*ageScaled||animal), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)), expand_re = TRUE)

memAccModel.2
```

## Memory accuracy with IQ

```{r memory acc maximal model w/IQ, eval = F}
#memory accuracy model including IQ
memAccModel.IQ <- mixed(memAcc ~ freqCondScaled * ageScaled * IQScaled  + (freqCondScaled|ID) + (freqCondScaled*ageScaled*IQScaled|animal), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))

memAccModel.IQ
#THIS MODEL PRODUCES CONVERGENCE ERRORS
```

```{r memory acc model w/IQ no correlations}
# remove correlations between random slopes and intercepts
memAccModel.IQ.2 <- mixed(memAcc ~ freqCondScaled * ageScaled * IQScaled  + (freqCondScaled||ID) + (freqCondScaled*ageScaled*IQScaled||animal), data = memDataCombined, family = "binomial", method = "LRT", control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)), expand_re = TRUE)

memAccModel.IQ.2 
```


```{r memory accuracy plots}
#first compute means of each condition
memAccMeans <- memDataCombined %>% group_by(freqCondFactor, ageGroup) %>% summarize(meanMemAcc = mean(memAcc, na.rm = TRUE), sdMemAcc = sd(memAcc, na.rm = TRUE), N = n(), seMemAcc = sdMemAcc/sqrt(N), min = meanMemAcc - seMemAcc, max = meanMemAcc + seMemAcc)

#first 30 trials only accuracy plot
memAccPlot <- ggplot(memAccMeans, aes(x = ageGroup, y = meanMemAcc, fill = freqCondFactor)) +
  geom_bar(stat = "identity", position = position_dodge(width = .9)) +
  geom_errorbar(data = memAccMeans, aes(x = ageGroup, ymin = min, ymax = max), position = position_dodge(width = .9), width = .2, stat = "identity") +
  coord_cartesian(ylim = c(0, .5)) + 
  xlab("Age Group") +
  ylab("Proportion Correct") +
  scale_fill_manual(values=c(color1, color2, color3)) +
  guides(fill = guide_legend(title = "Frequency Condition")) + 
  ggtitle("\n\nMemory Accuracy") +
  kate.theme
memAccPlot
```


# Relationship between structural learning and memory encoding
_As specified, we will now run a regression examining the effects of structural learning index on memory benefit score, to determine if participants who showed the most evidence of learning the animal frequencies also demonstrated the greatest effect of frequency condition on encoding._

```{r learning memory relationship}
#first, extract one line per subject
learnMemData <- memDataCombined %>% group_by(ID, IQ, Age, ageGroup) %>% summarize(learningIndex = mean(learningIndex, na.rm = TRUE), memBenefitIndex = mean(memBenefitIndex, na.rm = TRUE))

#scale Age, IQ, learning index
learnMemData$IQScaled <- scale_this(learnMemData$IQ)
learnMemData$ageScaled <- scale_this(learnMemData$Age)
learnMemData$learningIndexScaled <- scale_this(learnMemData$learningIndex)
```

## Structural learning model without IQ
```{r learning memory no IQ}
#run model without IQ
learnMem.lm <- lm(memBenefitIndex ~ ageScaled * learningIndexScaled, data = learnMemData)
pander(summary(learnMem.lm))
```

## Structural learning model with IQ
```{r learning memory with IQ}
#run model with IQ
learnMem.IQ.lm <- lm(memBenefitIndex ~ ageScaled * IQScaled * learningIndexScaled, data = learnMemData)
pander(summary(learnMem.IQ.lm))
```

## Plot: Correlation between frequency learning and memory
```{r learning memory plot}
# Plot the correlations
learnMemPlot <- ggplot(learnMemData, aes(x =learningIndex, y = memBenefitIndex)) +
  geom_point() +
  stat_smooth(method = "lm", color = color2) + 
  xlab("Structural Learning Index") + ylab ("Memory Benefit Index") +
kate.theme
learnMemPlot
```


## Plot: Interaction between age and IQ on memory benefit score
```{r age IQ mem benefit plot}
# Plot age and IQ relation
learnMemPlot2 <- ggplot(learnMemData, aes(x =IQ, y = memBenefitIndex, color = ageGroup, fill = ageGroup)) +
  geom_point() +
  geom_smooth(method = "lm", alpha = .1) + 
  scale_color_manual(values = c(color1, color2, color3), name = "Age Group") + 
  scale_fill_manual(values = c(color1, color2, color3), name = "Age Group") +
  xlab("IQ") + ylab ("Memory Benefit Index") +
kate.theme
learnMemPlot2
```

# Relationship between strategy use and memory encoding
_Finally, we will run a regression examining the effects of strategy use on memory benefit score. We will model the effect of subject strategy recognition (a 2-level categorical variable based on participant’s response (yes/no) to our question of whether they recognized that focusing on the more-frequent animals would be a good strategy) and age on their memory benefit score._

```{r strategy memory relationship}
#create data frame that has 1 row for each subject with age, ageGroup, IQ, mem benefit score, and strategy use
stratMemData <- memDataCombined %>% select(-c(animal, paFood, memRT, memResp, memAppearanceCount, foodSide, paResp, paRT, paTrial, memGridLocation, freqCond, Vocab, MR, meanPaAcc, include, learningIndex, memAcc, freqCondFactor, ageScaled, freqCondScaled))

#find unique rows
stratMemData <- unique(stratMemData)

#scale age and IQ
stratMemData$IQScaled <- scale_this(stratMemData$IQ)
stratMemData$ageScaled <- scale_this(stratMemData$Age)
```

## Strategy use regression without IQ
```{r strategy use without IQ}
#run regression without IQ
stratMem.lm <- lm(memBenefitIndex ~ ageScaled * GeneratedStrategy, data = stratMemData)
pander(summary(stratMem.lm))

```

## Strategy use regression with IQ
```{r strategy use with IQ}
#run regression with IQ
stratMem.IQ.lm <- lm(memBenefitIndex ~ ageScaled * IQScaled * GeneratedStrategy, data = stratMemData)
pander(summary(stratMem.IQ.lm))
```

## Strategy use by age group
```{r strategy use by age group}
#look at mean strategy use per age group
stratSummaryData <- stratMemData %>% group_by(ageGroup) %>% summarise(meanStratUse = mean(as.numeric(as.character(GeneratedStrategy))))

pander(stratSummaryData)
```